Title

### 2019-05-19 2_related_work.tex
better related work and related literature terminology
lil comments

\section{Related Work}
Adjusted MAT structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
\Cref{moessen}

@@

Using variable width lines to fit a precise amount of lines using the MAT. \cite{Ding2016a}
\Cref{ding}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{sources/related_work/ding.jpg}
\caption{asfd}
\label{ding}
\end{figure}

>>>>

\section{Related Work}
Adjusted MAT structure for only printing the outer wall, rest area to be filled using normal infill. \cite{Moesen2011}
\Cref{moessen}
Problem: small grey areas which are too small for the second wall lines.

@@

Using variable width lines to fit a precise amount of lines using the MAT.
\cite{Ding2016a} apply the method from \cite{kao1998optimal}.
\Cref{ding}

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{sources/related_work/ding.jpg}
\includegraphics[width=.7\columnwidth]{sources/related_work/kao.jpg}
\caption{Path planning strategies proposed by Kao (bottom) and employed in FDM by Ding et al (top).}
\label{ding}
\end{figure}
